Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-22 bbbq_article.tex
Process feedback

Because of these multiple and highly polymorphic MHC genes,
the number of pathogenic peptides that can be detected is increased,
as a wide variety of MHCs will be expressed,
each presenting their own subset of epitopes.
It is believed that this improves immunity at the population level, 
as mutations in a protein that disrupt a particular MHC presentation, 
so-called escape mutations, 
will not affect MHC presentation for all haplotypes \richel{Reference needed}.

@@

However, the physiological reason why peptides derived from TMHs 
would be presented more often than peptides 
stemming from soluble protein regions is unknown. 
One possibility is that the presentation of 
hydrophobic/TMH residues is evolutionary selected for, 
because TMHs are less prone to undergo escape mutation. 
One reason to expect such a reduced 
variability (and hence evolutionary conservation) in TMHs, 
is that these are restricted in their evolution 
by the functional requirement to span a lipid bilayer. 
Due to this, there are constraints in the types of amino acids 
that can be present in the TMH \richel{ref}. 
Therefore, the TMHs of pathogens 
might have a lower chance to develop an escape mutations, 
as many mutations will result in a dysfunctional TMH 
and render the protein inactive.

>>>>

Because of these multiple and highly polymorphic MHC genes,
the number of pathogenic peptides that can be detected is increased,
as a wide variety of MHCs will be expressed,
each presenting their own subset of epitopes.
It is believed that this improves immunity at the population level, 
as mutations in a protein that disrupt a particular MHC presentation, 
so-called escape mutations, 
will not affect MHC presentation for all haplotypes (\cite{sommer2005importance}).

@@

However, the physiological reason why peptides derived from TMHs 
would be presented more often than peptides 
stemming from soluble protein regions is unknown. 
One possibility is that the presentation of 
hydrophobic/TMH residues is evolutionary selected for, 
because TMHs are less prone to undergo escape mutation. 
One reason to expect such a reduced 
variability (and hence evolutionary conservation) in TMHs, 
is that these are restricted in their evolution 
by the functional requirement to span a lipid bilayer. 
Due to this, there are constraints in the types of amino acids 
that can be present in the TMH (\cite{jones1994model}). 
Therefore, the TMHs of pathogens 
might have a lower chance to develop an escape mutations, 
as many mutations will result in a dysfunctional TMH 
and render the protein inactive.
